---
title: "WEEK_4_PRESENTATION"
author: "Daiane Rodrigues"
date: "23 de junho de 2019"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Assigment week 4 

This is an apresentation about a submission for the Course Developing Data Product. 
The app that I build use the data mtcars and make a regression model. The response variable is Miles Gallon(mpg). You can choose which variables you want to test to predict MPG, you just have to select the box "Select the predictors". 

## Summary of the data set
Below You can see the summary of variables that you can use to predict MPG.  

```{r cars, echo = TRUE}
summary(mtcars)
```

## We want to predict Miles Gallon(mpg)

```{r pressure}
plot(mtcars$cyl,mtcars$mpg)
```

## APP 
You can see the app here: <https://daiane.shinyapps.io/Assigment_Week4/>.

And the Git Hub Repository here: <https://github.com/daiane1989/Assigment-Week-4---Developing-Data-Product/>.


